IFC Inside: A General Approach to Retrofitting Languages with Dynamic Information Flow Control

### 2014-04-11 paper/retrofit.tex
Fix two bugs pointed out by Stefan (sandbox should not evaluate e, and we don't need a barrier)
Signed-off-by: Edward Z. Yang <ezyang@cs.stanford.edu>

\begin{figure}
\begin{code}
lop  ::=  canFlowTo | lub | glb
iv   ::=  id | il | true | false | unit
ie   ::=  iv | ix | ie lop ie | getLabel | setLabel ie | getTaskId
       |  sandbox ie | send ie ie ie | recvf ix ix ie ie
iE   ::=  iHole | iE lop ie | iv lop iE | setLabel iE | sandbox iE
       |  send iE ie ie | send iv iE ie | send iv iv iE
io   ::=  (il, id ie)
Q    ::=  nil | io , Q
iS   ::=  emptyset | bracket iS (mapsto id Q)
\end{code}

@@

\begin{mathpar}
\inferrule[I-sandbox]
{ 
|iS' = bracket iS (mapsto id' nil)|\\
|tS' = klone(tS)|\\
|it1 = fullconf id il tS (iniE id')|\\
|itnew = fullconf id' il tS' (TI ie)|\\
|ap fresh id'|
}
{|
iconf iS (fullconf id il tS (iniEi (sandbox ie)), ldots)
.->
iS'; sched box (it1, ldots, itnew)
|}

>>>>

\begin{figure}
\begin{code}
lop  ::=  canFlowTo | lub | glb
iv   ::=  id | il | true | false | unit
ie   ::=  iv | ix | ie lop ie | getLabel | setLabel ie | getTaskId
       |  sandbox ie | send ie ie ie | recvf ix ix ie ie
iE   ::=  iHole | iE lop ie | iv lop iE | setLabel iE
       |  send iE ie ie | send iv iE ie | send iv iv iE
io   ::=  (il, id ie)
Q    ::=  nil | io , Q
iS   ::=  emptyset | bracket iS (mapsto id Q)
\end{code}

@@

\begin{mathpar}
\inferrule[I-sandbox]
{ 
|iS' = bracket iS (mapsto id' nil)|\\
|tS' = klone(tS)|\\
|it1 = fullconf id il tS (iniE id')|\\
|itnew = fullconf id' il tS' ie|\\
|ap fresh id'|
}
{|
iconf iS (fullconf id il tS (iniEi (sandbox ie)), ldots)
.->
iS'; sched box (it1, ldots, itnew)
|}
